The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-02-13 Paper/jaccardbaetica.tex
add new lines

\subsection{A potential indicator of Roman economy}

Stamps are the most studied in this type of amphorae. The fascination aroused by stamps has caused it to be one of the inscriptions with the most publications about its origin and meaning. Its endure in time become it an essential element that were used to mark amphorae during almost three centuries \citep{remesal_sellar_2016}. Frequently, they were marked mainly in handles but seldom in rims and body \citep{millet_anforas_1998}. 
The information of the stamps is shown in different forms and letter content and it seems that there was not a unique criterion. Stamps are mostly formed by a code of three letters and they can appear in a abbreviated form or complete and they are known as \textit{Tria Nomina} \citep{berni_millet_amphora_1996}.

%Many hypothesis involved the meaning of stamps. 
There is not a general consensus about the meaning of the stamps \citep{rodriguez_baetican_1998}. The meaning of these stamps could be identified based on two premises: content (olive oil) and context (amphora workshop). On the one hand, it seems that stamps could have been identified as the land owner of the olive groves \citep{rodriguez_economioleicola_1977}. On the other, they could belong to the owner of the making amphorae workshops or even a group of amphora workers (CITAR). Additionally, they have been related to a quality system \citep{callender} or a productin counting system \citep{berni_millet_epigrafianforica_2008}. In any case, the use of these stamps became in a good proxy to define somehow the system of working in the workshops.

>>>>

\subsection{A potential indicator of Roman economy: Dressel 20 stamps}

Stamps are the most studied in this type of amphorae. The fascination aroused by stamps has caused it to be one of the inscriptions with the most publications about its origin and meaning. Its endure in time become it an essential element that were used to mark amphorae during almost three centuries \citep{remesal_sellar_2016}. (Fig.\ref{amphora}).

\begin{figure}[htp]
	\centering
\includegraphics[scale=0.5]{figs/dressel20}
\caption{Dressel 20 were mostly marked with stamps of three letters called \textit{tria nomina}}
\label{amphora}
\end{figure}

Frequently, they were marked mainly in handles but seldom in rims and body \citep{millet_anforas_1998}. 
The information of the stamps is shown in different forms and letter content and it seems that there was not a unique criterion. Stamps are mostly formed by a code of three letters and they can appear in a abbreviated form or complete and they are known as \textit{Tria Nomina} \citep{berni_millet_amphora_1996}. Despite researchers identify stamps as a identity marks, there is not a general consensus about the meaning of the stamps \citep{rodriguez_baetican_1998}. Alike most Dressel 20 containers were not stamped being difficult to determinate.

They could be identified based on three premises: content (olive oil), context (amphora workshop) and subject (individuals involved). On the one hand, it seems that stamps could have been identified as the land owner of the olive groves \citep{rodriguez_economioleicola_1977}. On the other, they could belong to the owner of the making amphorae workshops or even a group of amphora workers (CITAR). Additionally, they have been related to a quality system \citep{callender} or a production counting system \citep{berni_millet_epigrafianforica_2008}. In any case, the use of these stamps became in a good proxy to define somehow the system of working in the workshops.
